\newpage
\section*{Acknowledgements}
        First and foremost, I would like to thank Dr. M. Sotomayor for his all around support and encouragement. Dr. Sotomayor provided me with a wonderful computer equipped with two fancy monitors, an expensive NVIDIA GPU, a powerful CPU, and the OS of my choice with which I was able to do some great work. He also helped fund my travel expenses and wrote some fantastic letters of recommendation that got me accepted to some conferences, and helped me secure a fellowship. In his lab I was able to present my work regularly and recevied great feedback from him and from the other lab members; which was an integral part of my development as a public speaker. In general, I couldn't have had an advisor who was more energetic, more encouraging, and dedicated to providing me with all the tools I  needed to perform great work.
        I also have to thank the members of the Sotomayor lab for attending my presentations, and for being such great company.
        I also have to thank Dr. E. Overman. Dr. Overman also wrote me wonderful letters of recommendation to get my travel expenses covered, and to make sure that I received a fellowship. Dr. Overman was my professor for the \emph{second} hardest class I ever took, and taught me to not pull my hair out when my homework had me stressed. I would have been bald. Even after watching me drown in his class, he still accepted me as his student and has since been a source of great mathematical, programming, and stylistic advice for this paper in your hands.
        I have to thank the Mathematics Department for their financial support. I received a generous fellowship during my first year at OSU, got to TA a great class during my third semester, and was then granted another ample fellowship for my last term. 

        
