\begin{thebibliography}{1}
\bibitem{Yoshi} K. Bambardekar et. al. Direct Laser Manipulation Reveals the Mechanics of Cell Contacts In Vivo \emph{PNAS} \textbf{112} 1416-1421.
\bibitem{Coupling} A. Barrat, et. al. Weighted evolving networks: coupling topology and weight dynamics. Arxiv. 
\bibitem{Large Cells} A. Beenakker. Two Dimensional Soap Froths and Polycrystalline Networks: Why Are Large Cells Many-Sided? \emph{Physica} \textbf{147A} 256-267.
\bibitem{MechanicalFeedback} Buchmann, A. Alber, M., Zartman, J. \emph{ Sizing it up: The mechanical feedback hypothesis of organ growth regulation.} Seminars in Cell and Developmental Biology, 2014.
\bibitem{Chaste Tutorial} \emph{Chaste Tutorial} \url{https://chaste.cs.ox.ac.uk/chaste/tutorials/release_2.1/UserTutorials.html}
\bibitem{Drasdo} Drasdo, D. \emph{Bucking Instabilities of One Layered Growing Tissues.} Physical Review Letters 84.
\bibitem{Drasdo2} D. Drasdo. Modeling the Interplay of Generic and Genetic Mechanisms in Cleavage, Blastulation, and Glasulation. \emph{Developmental Dynamics} \textbf{219} 182-191.
\bibitem{Random} J. M. Drouffe, C. Itzykson. Random Geometry and the statistics of two-dimensional cells. \emph{Nuclear Physics} \textbf{B235} 45-53.
\bibitem{Renewal} B. Dubertret, N. Rivier. The Renewal of the Epidermis: A Topological Mechanism. \emph{Biophysical Journal} \textbf{73} 38-44.
\bibitem{DurandStone} Durand, M., Stone, H. Relaxation Time of the Topological T1 process in a Two Dimensional Foam. arXiv.0
\bibitem{Epithelium}\emph{Epithelial Tissues} \url{http://www.botany.uwc.ac.za/sci_ed/grade10/mammal/epithelial.htm}
\bibitem{Farhadifar} Farhadifar, R., Roper, J., Algouy, B., Eaton, S., Jullcher, F. The Influence of Cell Mechanics, Cell-Cell Interactions, and Proliferation on Epithelial Packing. \emph{Current Biology} \textbf{17} 2095-2104. (2007) 
\bibitem{Vertex Models} Fletcher, A. , Osterfield, M., Baker, R., Shvartsman, S. \emph{Vertex Models of Epithelial Morphogenesis.} Biophysical Journal 106, June 2014.
\bibitem{ChasteMain} Fletcher, A., Osborne, J., Maini, P, Gavaghan, D. \emph{Implementing vertex dynamics models of cell populations in biology within a consitent computational framework.} Prog. Biophys. Mol. Biol. 113: 299 - 326.
\bibitem{Overview} Gibson, W., Gibson, M. \emph{Cell Topology, Geometry, and Morphogenesis  in Proliferating Epithelia.} Current Topics in Developmental Biology \textbf{89} 87-114. (2009)
\bibitem{Kinetics Glazier} J. Glazier, D. Weaire. The kinetics off cellular patterns. \emph{Condensed Matter} \textbf{4} 1867-1894.
\bibitem{Relaxation of T1} P. Grassia, C. Oguey, R. Satomi. Relaxation of the topological T1 process in a two-dimensional foam. \emph{The European Physical Journal E} \textbf{35} (2012)
\bibitem{Dirichlet Domains} H. Honda. Description of Cellular Patterns by Dirichlet Domains: The Two-Dimensional Case. \emph{Journal of Theoretical Biology} \textbf{72} 523-543. (1978)
\bibitem{Cell Division} H. Honda, H. Yamanaka, M. Dan-Sohkawa. A Computer Simulation of Geometrical Configurations During Cell Division. \emph{Journal of Theoretical Biology} \textbf{106} 423-435. (1984)
\bibitem{Shape Formation} Honda, H. Essence of Shape Formation in Animals. \emph{Forma}, \textbf{27} S1-S8. (2012)
\bibitem{1989 Kawasaki} K. Kawasaki, T. Nagai, K. Nakashima. Vertex models for two-dimensional grain growth. \emph{Philisophical Magazine Part B} \textbf{60} 399 - 421. (1989)
\bibitem{rose} K. Liu, S. Ernst, V. Lecaudey, O. Ronneberger. Epithelial Rosette Detection in Microscopic Images.
\bibitem{CellSize} Marshall et. al. What Determines Cell Size? \emph{BMC Biology} \textbf{10} (2012)
\bibitem{Correllations} M.F. Miri, C. Oguey. Topological Correlations and Asymptotic Freedom in Cellular Aggregates. \emph{Colloids and Surfaces A} \textbf{309} 107-111.
\bibitem{Two-Dimensional Patterns} T. Nagai, K. Kawasaki, K. Nakamura. Vertex Dynamics of Two-Dimensional Cellular Patterns. \emph{Journal of the physical sciences of Japan} \textbf{57} 2221-2224.
\bibitem{Dyn} T. Nagai, K. Kawasaki. Dynamics of Cellular Pattern in Two Dimensions. \emph{Research of Pattern Formation} 389-400
\bibitem{Epithelial Topology} R. Nagpal, A. Patel, M. Gibson. Epithelial Topology. \emph{BioEssays} \textbf{30} 260-266. (2008)
\bibitem{Scaling Behavior} K. Nakashima, T. Nagai, K. Kawasaki. Scaling Behavior of Two-Dimensional  Domain Growth: Computer Simulation of Vertex Models. \emph{Journal of Statistical Physics} \textbf{57} 759-787. (1989)
\bibitem{TopStruct2DUnordered} Ohlenbusch, H.M., Aste, T. Dubertret, B., Rivier, N. The Topological Structure of 2D Disordered Cellular Structures. arXiv.
\bibitem{Okuda1} S.Okuda et. al. Reversible Network Reconnection Model for Simulating Large Deformation in Dynamic Tissue Morphogenesis. \emph{Biomech Model Mechanobiol} \textbf{12} 627-644 (2013)
\bibitem{epitheliumImage} \url{http://www.millerplace.k12.ny.us/webpages/lmiller/photos/636532/Epithelial\%20TissueTypes.bmp}
\bibitem{tutorvista} Potential Energy Graph \url{http://images.tutorvista.com/content/work-energy-power/potential-energy-variation.gif}
\bibitem{Soap} Weaire, D. and Rivier, N. \emph{Soap, Cells, and Statistics}
\bibitem{Udacity} Luebke, D. and Owens, J. \emph{Intro to Parallel Programming} \url{https://www.udacity.com/course/cs344} 2013.
\bibitem{HondaNagai} Nagai, T. Honda, H. \emph{A dynamic model for the formation of epithelial tissues.} Philisohpical Magazine, Pt. B. Vol 81, Issue 7, 2001.
\bibitem{Plasticity} N. Rivier et. al. Plasticity and topological defects in cellular structures: Extra matter, folds, and crab moulting. \emph{Colloids and Surfaces A} \textbf{263} 39 - 45.
\bibitem{Morphogen} Restrepo, S., Zartman, J. , and Basler, K. \emph{ Coordination of Patterning and Growth by the Morphogen DPP} Current Biology 24, 245- 255
\bibitem{Optimization} K. Satake, H. Honda. Evolution Towards the Solution of the Shape Optimization Problem. \emph{Forma} \textbf{17} 253-274.
\bibitem{ZebraFish} C. Schroter et. al. Topology and Dynamics of the Zebrafish Segmentation Clock Core Circuit. \emph{PLOS Biology} \textbf{10} Issue 7.
\bibitem{Stavans}J. Stavans. Evolution of two-dimensional cellular structures: The Soap Froth. \emph{Physica A} \textbf{194} 307-314,
\bibitem{Topological Models} R. Thom. Topological Models in Biology. \emph{Topology} \textbf{8} 313- 315 (1969)
\bibitem{Checkers} H. Yamanaka and H. Honda. A checkerboard pattern manifested by the oviduct epithelium of the Japanese Quail. \emph{Int. J. Dev. Biol.} \textbf{34} 377-383.
\end{thebibliography}
